### 2015-08-10 rscripts/data_review.Rmd
minor tweaks, mostly reading atm

```{r, echo=FALSE, include=FALSE}
req.packages <- c("data.table", "ggplot2", "reshape2", "grid", "scales", "animation")
need.pkgs <- req.packages[!sapply(req.packages, require, character.only = T)]
if (length(need.pkgs) != 0) install.packages(need.pkgs, dependencies = T)
```

@@

prev.dt <- cross_group(censor.dt[offset <= login_day & login_day < (offset+window)], duration_breaks, daily_login_breaks)
saveGIF(for (start in seq(offset+slide, censor.dt[,max(login_day)]-window, by=slide)) {
  timeslice <- censor.dt[start <= login_day & login_day < (start+window)]
  cross_data.dt <- cross_group(timeslice, duration_breaks, daily_login_breaks)
  plotting.dt <- merge(cross_data.dt, prev.dt, by=c("location_id", "group.duration", "group.login"), all=T, suffixes = c("",".prev"))
  print(base_plot +
    geom_point(data = plotting.dt[!is.na(membership.duration.prev)], na.rm = TRUE) +
    geom_point(data = plotting.dt[is.na(membership.duration.prev)]) +
    geom_point(
      data=plotting.dt[
        is.na(membership.duration),
        list(
          membership.duration=membership.duration.prev,
          membership.login=membership.login.prev
        ),
        by=list(group.duration, group.login, location_id)
      ], color="black", shape = 1)
  )
  prev.dt <- cross_data.dt
})
```

>>>>

```{r, echo=FALSE, include=FALSE}
req.packages <- c("data.table", "ggplot2", "reshape2", "grid", "scales", "animation", "randomForest")
need.pkgs <- req.packages[!sapply(req.packages, require, character.only = T)]
if (length(need.pkgs) != 0) install.packages(need.pkgs, dependencies = T)
```

@@

prev.dt <- cross_group(censor.dt[offset <= login_day & login_day < (offset+window)], duration_breaks, daily_login_breaks)
# saveGIF(for (start in seq(offset+slide, censor.dt[,max(login_day)]-window, by=slide)) {
#   timeslice <- censor.dt[start <= login_day & login_day < (start+window)]
#   cross_data.dt <- cross_group(timeslice, duration_breaks, daily_login_breaks)
#   plotting.dt <- merge(cross_data.dt, prev.dt, by=c("location_id", "group.duration", "group.login"), all=T, suffixes = c("",".prev"))
#   print(base_plot +
#     geom_point(data = plotting.dt[!is.na(membership.duration.prev)], na.rm = TRUE) +
#     geom_point(data = plotting.dt[is.na(membership.duration.prev)]) +
#     geom_point(
#       data=plotting.dt[
#         is.na(membership.duration),
#         list(
#           membership.duration=membership.duration.prev,
#           membership.login=membership.login.prev
#         ),
#         by=list(group.duration, group.login, location_id)
#       ], color="black", shape = 1)
#   )
#   prev.dt <- cross_data.dt
# })
```
